Handling Recursion in Generic Programming Using Closed Type Families

### 2018-08-24 lncs-paper.tex
Typos

\textbf{Category:} full research paper.

\textbf{Studentship:} both authors are students.

@@

Unfortunately, this approach, albeit working well for datatypes defined like \K{PolyRec a}, becomes unsuitable for nested datatypes, such as one below:
\begin{lstlisting}
data Nested a = Epsilon | Nest a (Nested [a])
\end{lstlisting}
The culprit is the constraint \K{All2 (CaseRecShow a) (Code a)} that now turns out to be a root of nonterminating computation of the \K{GShow} constraint for K{[a]}, K{[[a]]}, and so on ad infinitum.

>>>>

@@

Unfortunately, this approach, albeit working well for datatypes defined like \K{PolyRec a}, becomes unsuitable for nested datatypes, such as one below:
\begin{lstlisting}
data Nested a = Epsilon | Nest a (Nested [a])
\end{lstlisting}
The culprit is the constraint \K{All2 (CaseRecShow a) (Code a)} that now turns out to be a root of nonterminating computation of the \K{GShow} constraint for \K{[a]}, \K{[[a]]}, and so on ad infinitum.
